An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-14 EconGrowth-R-Functions.Rnw
Now including a parameters graph for CES without energy.

<<AIC_Table_Functions, eval=TRUE>>=
###############################
# Creates an xtable object that holds the AIC values for each parameter estimation that we include.
##
createAICTable <- function(){
  ######################
  # Single-factor models
  ######################
  # Single-factor with K
  sfKModels <- lapply(countryAbbrevs, singleFactorModel, factor="K")
  aicSFk <- data.frame(lapply(sfKModels, AIC))
  rownames(aicSFk) <- "SF$k$"
  # Single-factor with L
  sfLModels <- lapply(countryAbbrevs, singleFactorModel, factor="L")
  aicSFl <- data.frame(lapply(sfLModels, AIC))
  rownames(aicSFl) <- "SF$l$"
  # Single-factor with Q
  sfQModels <- lapply(countryAbbrevs, singleFactorModel, factor="Q")
  aicSFq <- data.frame(lapply(sfQModels, AIC))
  rownames(aicSFq) <- "SF$q$"
  # Single-factor with X
  sfXModels <- lapply(countryAbbrevs, singleFactorModel, factor="X")
  aicSFx <- data.frame(lapply(sfXModels, AIC))
  rownames(aicSFx) <- "SF$x$"
  # Single-factor with U
  aicSFu <- cbind(US=AIC(singleFactorModel("US", "U")), 
                  UK=AIC(singleFactorModel("UK", "U")), 
                  JP=AIC(singleFactorModel("JP", "U")),
                  CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA) #No U data for these countries.
  rownames(aicSFu) <- "SF$u$"
  ######################
  # Cobb-Douglas models
  ######################
  # Cobb-Douglas without energy
  cdModels <- lapply(countryAbbrevs, cobbDouglasModel)
  aicCD <- data.frame(lapply(cdModels, AIC))
  rownames(aicCD) <- "CD"
  # Cobb-Douglas with Q
  cdQModels <- lapply(countryAbbrevs, cobbDouglasModel, energyType="Q")
  aicCDq <- data.frame(lapply(cdQModels, AIC))
  rownames(aicCDq) <- "CD$q$"
  # Cobb-Douglas with X
  cdXModels <- lapply(countryAbbrevs, cobbDouglasModel, energyType="X")
  aicCDx <- data.frame(lapply(cdXModels, AIC))
  rownames(aicCDx) <- "CD$x$"
  # Cobb-Douglas with U
  aicCDu <- cbind(US=AIC(cobbDouglasModel("US", "U")), 
                  UK=AIC(cobbDouglasModel("UK", "U")), 
                  JP=AIC(cobbDouglasModel("JP", "U")),
                  CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA) #No U data for these countries.
  rownames(aicCDu) <- "CD$u$"
  ######################
  # CES models
  ######################
# At present, this AIC for CES code is not working. Perhaps because the CES model from the cesEst function
# in the micEcon package does not provide its data in the correct format for the AIC function?
# --Matthew Kuperus Heun, 10 April 2013.
#   # CES with Q
#   cesQModels <- lapply(countryAbbrevs, cesModel, energyType="Q")
#   aicCESq <- data.frame(lapply(cesQModels, AIC))
#   rownames(aicCESq) <- "CES$q$"
#   # CES with X
#   cesXModels <- lapply(countryAbbrevs, cesModel, energyType="X")
#   aicDEXx <- data.frame(lapply(cesXModels, AIC))
#   rownames(aicCESx) <- "CES$x$"
#   # CES with U
#   aicCESu <- cbind(US=AIC(cesModel("US", "U")), 
#                   UK=AIC(cesModel("UK", "U")), 
#                   JP=AIC(cesModel("JP", "U")),
#                   CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA) #No U data for these countries.
#   rownames(aicCESu) <- "CES$u$"
  ######################
  # LINEX models
  ######################
  # LINEX with Q
  linexQModels <- lapply(countryAbbrevs, linexModel, energyType="Q")
  aicLINEXq <- data.frame(lapply(linexQModels, AIC))
  rownames(aicLINEXq) <- "LINEX$q$"
  # LINEX with X
  linexXModels <- lapply(countryAbbrevs, linexModel, energyType="X")
  aicLINEXx <- data.frame(lapply(linexXModels, AIC))
  rownames(aicLINEXx) <- "LINEX$x$"  
  # LINEX with U
  aicLINEXu <- cbind(US=AIC(linexModel("US", "U")), 
                  UK=AIC(linexModel("UK", "U")), 
                  JP=AIC(linexModel("JP", "U")),
                  CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA) #No U data for these countries.
  rownames(aicLINEXu) <- "LINEX$u$"

  # Create the data.frame table
  out <- rbind(aicSFk, aicSFl, aicSFq, aicSFx, aicSFu, 
               aicCD, aicCDq, aicCDx, aicCDu, 
               aicLINEXq, aicLINEXx, aicLINEXu) 
#   out <- rbind(aicSFk, aicSFl, aicSFq, aicSFx, aicSFu, 
#                aicCD, aicCDq, aicCDx, aicCDu, 
#                aicCESq, aicCESx, aicCESu, 
#                aicLINEXq, aicLINEXx, aicLINEXu) 
  # Create the xtable with caption and label
  out <- xtable(out, caption="AIC values for all models.", label="tab:AICTable", digits=1)
  return(out)
}
@

>>>>

<<AIC_Table_Functions, eval=TRUE>>=
###############################
# Creates an xtable object that holds the AIC values for each parameter estimation that we include.
createAICTable <- function(){
  ######################
  # Single-factor models
  ######################
  # Single-factor with K
  sfKModels <- lapply(countryAbbrevs, singleFactorModel, factor="K")
  aicSFk <- data.frame(lapply(sfKModels, AIC))
  rownames(aicSFk) <- "SF$k$"
  # Single-factor with L
  sfLModels <- lapply(countryAbbrevs, singleFactorModel, factor="L")
  aicSFl <- data.frame(lapply(sfLModels, AIC))
  rownames(aicSFl) <- "SF$l$"
  # Single-factor with Q
  sfQModels <- lapply(countryAbbrevs, singleFactorModel, factor="Q")
  aicSFq <- data.frame(lapply(sfQModels, AIC))
  rownames(aicSFq) <- "SF$q$"
  # Single-factor with X
  sfXModels <- lapply(countryAbbrevs, singleFactorModel, factor="X")
  aicSFx <- data.frame(lapply(sfXModels, AIC))
  rownames(aicSFx) <- "SF$x$"
  # Single-factor with U
  aicSFu <- cbind(US=AIC(singleFactorModel("US", "U")), 
                  UK=AIC(singleFactorModel("UK", "U")), 
                  JP=AIC(singleFactorModel("JP", "U")),
                  CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA) #No U data for these countries.
  rownames(aicSFu) <- "SF$u$"
  ######################
  # Cobb-Douglas models
  ######################
  # Cobb-Douglas without energy
  cdModels <- lapply(countryAbbrevs, cobbDouglasModel, energyType=NA)
  aicCD <- data.frame(lapply(cdModels, AIC))
  rownames(aicCD) <- "CD"
  # Cobb-Douglas with Q
  cdQModels <- lapply(countryAbbrevs, cobbDouglasModel, energyType="Q")
  aicCDq <- data.frame(lapply(cdQModels, AIC))
  rownames(aicCDq) <- "CD$q$"
  # Cobb-Douglas with X
  cdXModels <- lapply(countryAbbrevs, cobbDouglasModel, energyType="X")
  aicCDx <- data.frame(lapply(cdXModels, AIC))
  rownames(aicCDx) <- "CD$x$"
  # Cobb-Douglas with U
  aicCDu <- cbind(US=AIC(cobbDouglasModel("US", "U")), 
                  UK=AIC(cobbDouglasModel("UK", "U")), 
                  JP=AIC(cobbDouglasModel("JP", "U")),
                  CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA) #No U data for these countries.
  rownames(aicCDu) <- "CD$u$"
  ######################
  # CES models
  ######################
# At present, this AIC for CES code is not working. Perhaps because the CES model from the cesEst function
# in the micEcon package does not provide its data in the correct format for the AIC function?
# --Matthew Kuperus Heun, 10 April 2013.
#   # CES with Q
#   cesQModels <- lapply(countryAbbrevs, cesModel, energyType="Q")
#   aicCESq <- data.frame(lapply(cesQModels, AIC))
#   rownames(aicCESq) <- "CES$q$"
#   # CES with X
#   cesXModels <- lapply(countryAbbrevs, cesModel, energyType="X")
#   aicDEXx <- data.frame(lapply(cesXModels, AIC))
#   rownames(aicCESx) <- "CES$x$"
#   # CES with U
#   aicCESu <- cbind(US=AIC(cesModel("US", "U")), 
#                   UK=AIC(cesModel("UK", "U")), 
#                   JP=AIC(cesModel("JP", "U")),
#                   CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA) #No U data for these countries.
#   rownames(aicCESu) <- "CES$u$"
  aicCES  <- data.frame(US=NA, UK=NA, JP=NA, CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA)
  rownames(aicCES) <- "CES"
  aicCESq <- data.frame(US=NA, UK=NA, JP=NA, CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA)
  rownames(aicCESq) <- "CES$q$"
  aicCESx <- data.frame(US=NA, UK=NA, JP=NA, CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA)
  rownames(aicCESx) <- "CES$x$"
  aicCESu <- data.frame(US=NA, UK=NA, JP=NA, CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA)
  rownames(aicCESu) <- "CES$u$"
  ######################
  # LINEX models
  ######################
  # LINEX with Q
  linexQModels <- lapply(countryAbbrevs, linexModel, energyType="Q")
  aicLINEXq <- data.frame(lapply(linexQModels, AIC))
  rownames(aicLINEXq) <- "LINEX$q$"
  # LINEX with X
  linexXModels <- lapply(countryAbbrevs, linexModel, energyType="X")
  aicLINEXx <- data.frame(lapply(linexXModels, AIC))
  rownames(aicLINEXx) <- "LINEX$x$"  
  # LINEX with U
  aicLINEXu <- cbind(US=AIC(linexModel("US", "U")), 
                  UK=AIC(linexModel("UK", "U")), 
                  JP=AIC(linexModel("JP", "U")),
                  CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA) #No U data for these countries.
  rownames(aicLINEXu) <- "LINEX$u$"

  # Create the data.frame table
  out <- rbind(aicSFk, aicSFl, aicSFq, aicSFx, aicSFu, 
               aicCD, aicCDq, aicCDx, aicCDu, 
               aicCES, aicCESq, aicCESx, aicCESu, 
               aicLINEXq, aicLINEXx, aicLINEXu) 
  # Create the xtable with caption and label
  out <- xtable(out, caption="AIC values for all models.", label="tab:AICTable", digits=1)
  return(out)
}
@

### 2013-04-14 EconGrowth.Rnw
Nearly have the presentation also working after changing all of the code for signifying that you want a model without energy to use energyType=NA.
Now including a parameters graph for CES without energy.

\item{Heun: Convert the presentation to use energyType=NA for models without energy}

@@

      \item Add a CES model without energy option (unspecified energyType parameters means CES without energy)
          \item{Extract CES without energy parameters from the ``without energy'' models and correctly name them: $\sigma \rightarrow \sigma_1$, $\rho \rightarrow \rho_1$, $\delta \rightarrow \delta_1$}
          \item{Add CES without energy parameters to tables of results in the appendix}
          \item{Create a CES without energy parameters graphs (with CIs) in the paper}

@@

@@

@@

<<CES_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=

# print(cesData("US"))
# print(cesCountryRow("US"))
# print(cesCountryRowsForParamsGraph("US"))
# print(cesParamsTableDF())

# Testing null and missing

testMissing <- function(param){
  print(paste("missing(param) =", missing(param)))
  print(paste("is.na(param) =", is.na(param)))
  print(paste("is.null(param) =", is.null(param)))
  print(paste("param =", param))
}

# testMissing()
# testMissing(NA)
# testMissing(NULL)
# testMissing("")

@

@@

The following tables provide results for parameters in CES models.

>>>>

@@

@@

      \item{\st{Add a CES model without energy option (energyType=NA means CES without energy)}}
          \item{\st{Create a CES without energy parameters graphs (with CIs) in the paper}}
          \item{\st{Extract CES without energy parameters from the ``without energy'' models and correctly name them: $\sigma \rightarrow \sigma_1$, $\rho \rightarrow \rho_1$, $\delta \rightarrow \delta_1$}}
          \item{\st{Add CES without energy parameters to tables of results in the appendix}}

@@

\item{\st{Heun: Convert the presentation to use energyType=NA for models without energy}}

@@

Figure \ref{fig:CES_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (without energy).

<<CES_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType=NA)
@

@@

The following tables provide results for parameters in CES models with and without energy terms.
